Hypertension and microbiome

### 2019-02-11 articletwo.Rmd
Minor

ggsave(file = "cache/pca.p2.png", plot = p2, height = 8, width = 8, dpi = 300)

```

@@

```{r Write figure 5}
fig4head <- "Bacteria causing dysentery and diarrhea contribute to third principal component"
fig4foot <- sprintf("Top 20 bacterial contributors to third principal coordinate at species level. Centered log ratio transform is performed for the compositional data. Third principal component explain %.1f%% of the total variation. Plasmid DNA is denoted using star.", pca.percentage[3])
writeimage(doc, 5, "cache/pca.pc3.png", fig4head, fig4foot)
```

>>>>

ggsave(file = "cache/pca.p2.png", plot = p2, height = 8, width = 8, dpi = 300) 
```

```{r Write figure 5}
fig4head <- "P2"
fig4foot <- ""
writeimage(doc, 4, "cache/pca.p2.png", fig4head, fig4foot)
```

@@

```{r Write figure 5}
fig5head <- "Bacteria causing dysentery and diarrhea contribute to third principal component"
fig5foot <- sprintf("Top 20 bacterial contributors to third principal coordinate at species level. Centered log ratio transform is performed for the compositional data. Third principal component explain %.1f%% of the total variation. Plasmid DNA is denoted using star.", pca.percentage[3])
writeimage(doc, 5, "cache/pca.pc3.png", fig5head, fig5foot)
```
